\pdftitle

### 2017-05-16 maxNt.tex
worked on Intro

Recent advances in electrophysiological recordings allow to
 study the collective behavior of large population of neurons 
in relation to stimuli and bahavioral tasks [\cite]. Huge amount of parallel
 recordings from hundreds of neurons, available today, is accompanied by
 the statistical challenges to shed light on the mechanism behind neuronal coding. 
The principle of \me\ was proposed as a way to overcome these challenges by constructing a full description of the 
neuronal firing patterns based on only first and second order statistics of the observed data [\cite].

>>>>

Recent advances in electrophysiological recordings allow to
 study the activity of large population of neurons 
in relation to stimuli and bahavioral tasks [\cite]. Huge amount of parallel
 recordings from hundreds of neurons, available today, is accompanied by
 the statistical challenges to be employed for shedding light on the mechanism behind neuronal coding. 
The principle of \me\ was proposed as a way to overcome these challenges by constructing a full description of the 
neuronal firing patterns. The \me\ method exploits only first and second
order statistics of the observed data and construct a least structured or
a \enquote{maximally noncommital} probability distribution of firing patterns [\cite].
